---
title: "Maps"
author: 'Moritz Burger & Noémie Wellinger'
date: "`r Sys.Date()`"
output: html_document
---

```{r libraries, include = F}
library(caret)
library(dplyr)
library(ggmap)
library(ggplot2)
```

```{r read_data, include = F}
Summary <- read.csv("../data/Analysis 2023/Summary_T_2023_JJA.csv")
head(Summary)

data<-read_csv(paste0("../data/Analysis 2023/Rawdata_T_2023_", time_range, ".csv"))

# shift the hours, so that the night is not cut in half
data <- data |>
  mutate(Time = as.POSIXct(Time, format = "%Y-%m-%d %H:%M", tz = "Europe/Zurich"))
```

 
```{r preprocess, include=F}

```

```{r}
Summer22_all<-
  ggmap(map) +
  geom_point(data=data, aes(y=Latitude, x=Longitude, fill=UHI_all),pch=21, size=4, color="black") +
  labs(title="UHI Summer 2022 all", y="", x="") +
  scale_fill_gradientn(colors=colorscheme,limits=c(-3,3), name="")+
  theme(legend.text=element_text(size=10), plot.title=element_text(size=16, hjust=0.5), axis.text=element_blank(), axis.ticks=element_blank(),
        legend.position="top", legend.key.width = unit(2, "cm"))
```


Summer22_all<-
  ggmap(map) +
  geom_point(data=data, aes(y=Latitude, x=Longitude, fill=UHI_all),pch=21, size=4, color="black") +
  labs(title="UHI Summer 2022 all", y="", x="") +
  scale_fill_gradientn(colors=colorscheme,limits=c(-3,3), name="")+
  theme(legend.text=element_text(size=10), plot.title=element_text(size=16, hjust=0.5), axis.text=element_blank(), axis.ticks=element_blank(),
        legend.position="top", legend.key.width = unit(2, "cm"))

Summer22_night<-
  ggmap(map) +
  geom_point(data=data, aes(y=Latitude, x=Longitude, fill=UHI_night),pch=21, size=4, color="black") +
  labs(title="UHI Summer 2022 night", y="", x="") +
  scale_fill_gradientn(colors=colorscheme,limits=c(-3,3), name="")+
  theme(legend.text=element_text(size=10), plot.title=element_text(size=16, hjust=0.5), axis.text=element_blank(), axis.ticks=element_blank(),
        legend.position="top", legend.key.width = unit(2, "cm"))

Summer22_day<-
  ggmap(map) +
  geom_point(data=data, aes(y=Latitude, x=Longitude, fill=UHI_day),pch=21, size=4, color="black") +
  labs(title="UHI Summer 2022 day", y="", x="") +
  scale_fill_gradientn(colors=colorscheme,limits=c(-3,3), name="")+
  theme(legend.text=element_text(size=10), plot.title=element_text(size=16, hjust=0.5), axis.text=element_blank(), axis.ticks=element_blank(),
        legend.position="top", legend.key.width = unit(2, "cm"))


ggsave("Summer22_all.jpg", Summer22_all, path="D:/PhD_Moritz/Stadt Bern_Austausch/Berechnungen/Kennzahlen pro Sommer/2022", height=8.5, width=8)
ggsave("Summer22_night.jpg", Summer22_night, path="D:/PhD_Moritz/Stadt Bern_Austausch/Berechnungen/Kennzahlen pro Sommer/2022", height=8.5, width=8)
ggsave("Summer22_day.jpg", Summer22_day, path="D:/PhD_Moritz/Stadt Bern_Austausch/Berechnungen/Kennzahlen pro Sommer/2022", height=8.5, width=8)
